Portable Visible Spectrophotometer for Glucose Microdroplet Measurements in Digital Microfluidics System

### 2022-12-09 paper-kelompok/main.tex
render

    \begin{equation}
    A=-\log10{T}=\log{\frac{{I_{0}}{I}}}
    \label{absorbance}
    \end{equation}

Transmittance \emph{T} is the percentage of incident radiation that the sample transmits, \emph{I_{0}} denotes the intensity of polychromatic light entering the sample, and \emph{I} denotes the intensity of light leaving the sample;
Absorbance is directly proportional to the path length \emph{l} through the medium and the concentration \emph{c} of the absorbing substance for monochromatic radiation.
Beer-Lambert's law, expressed in Equation (\ref{beer-lambert}), serves as the basis for quantitative analyses using both atomic and molecular absorption measurements (\emph{\epsilon} is the molar attenuation coefficient)\cite{b4}.

@@

where m is the line's slope (gradient) and b is the constant representing the linear equation's y-intercept.

@@

\begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.25]{glucosetransmittanceALL.png}}
    \caption{Glucose 40 ug/ml Transmittance}
    \label{glucose_transmittance_all}
    \end{figure}

@@

\begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.25]{glucose_peakwavelength.png}}
    \caption{Glucose 40 ug/ml Peak Wavelengths}
    \label{glucose_peak_wavelength}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.6]{lcd-spec.JPEG}}
    \caption{The display of the result pages of a spectrum-mode measurement}
    \label{lcd-spec}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.6]{lcd-conc.JPEG.}}
    \caption{The display of the table page of a quantization-mode curve}
    \label{lcd-conc}
    \end{figure}

>>>>

    \begin{equation}
    A=-\log10{T}=\log{\frac{I_{0}}{I}}
    \label{absorbance}
    \end{equation}

Transmittance $T$ is the percentage of incident radiation that the sample transmits, $I_0$ denotes the intensity of polychromatic light entering the sample, and $I$ denotes the intensity of light leaving the sample;
Absorbance is directly proportional to the path length $l$ through the medium and the concentration $c$ of the absorbing substance for monochromatic radiation.
Beer-Lambert's law, expressed in Equation (\ref{beer-lambert}), serves as the basis for quantitative analyses using both atomic and molecular absorption measurements ($\epsilon$) is the molar attenuation coefficient)\cite{b4}.

@@

where $m$ is the line's slope (gradient) and $b$ is the constant representing the linear equation's y-intercept.

@@

\begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{glucosetransmittanceALL.png}}
    \caption{Glucose 40 ug/ml Transmittance}
    \label{glucose_transmittance_all}
    \end{figure}

@@

\begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.5]{glucose_peakwavelength.png}}
    \caption{Glucose 40 ug/ml Peak Wavelengths}
    \label{glucose_peak_wavelength}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.06]{lcd-spec.JPEG}}
    \caption{The display of the result pages of a spectrum-mode measurement}
    \label{lcd-spec}
    \end{figure}

@@

    \begin{figure}[htbp]
    \centerline{\includegraphics[scale=0.06]{lcd-conc.jpeg}}
    \caption{The display of the table page of a quantization-mode curve}
    \label{lcd-conc}
    \end{figure}
